### 2022-02-09 Journal1/Response (21-10-2019)/Response.tex

[4] Mesiti, Fabio, and Ilangko Balasingham. ``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol. 31, no. 12, pp. 695-704, 2013.

[5] N. Rouach, E. Avignone, W. Même, A. Koulakoff, L. Venance, F. Blomstrand, and C. Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol. 94, no. 7-8, pp. 457-475, 2002.

[6] J. Hjorth, K. T. Blackwell, and J. Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J. Neuroscience, vol. 29, no. 16, pp. 5276-5286, 2009.

[7] R. D. Traub, M. A. Whittington, E. H. Buhl, F. E. N. LeBeau, A. Bibbig, S. Boyd, H. Cross, and T. Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol. 42, no. 2, pp. 153-170, 2001.
\\
\hline
\end{longtable}

\clearpage
In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
stimulation with an array of 50 NW connections per neuron. The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations. We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.

\textbf{Gap Junction Interface [4]}:

With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells. Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity. In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted. This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.

\begin{figure}[H]
\centering
\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
\label{new_1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!45}
\textbf{Reviewer 4} \\
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 1:} ``The description of  ``unhealthy neuron'' or ``neurons that have lost their ability to communicate'' and the nano-machines to connect them seems to provide a possible future application to the communication channel model proposed. What the manuscript is not fully analyzing in the opinion of this reviewer is exactly how the nano-machines could utilize this model from an engineering perspective. If this connection is not considered to be the focus and therefore was not researched, then the consideration should be made to remove the concept of nano-machines from the ``System Model'' section (and subsequent sections) and use it merely for motivating the model.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of our manuscript and for
the thoughtful comments and constructive suggestions, which helped us to improve
the quality of this manuscript. We hope that the modifications that we have made to the manuscript, and the
responses that we have provided herein will alleviate the reviewer concerns.

In recent years, engineering applications of nano-technology have also been investigated with increasing interest
for the design of bio-inspired intelligent nano-devices or nano-machines connected in a network. In this manuscript, we considered the concept of nano-machines in the proposed system model according to the reported efforts to interface the neuron's body
with synthetic nano-scale materials in the literature. We provide a brief explanation in the following. We refer to the following list of references in our explanation in this comment:

\clearpage
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.

[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.

[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.

[4] Mesiti, Fabio, and Ilangko Balasingham. ``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol. 31, no. 12, pp. 695-704, 2013.

[5] N. Rouach, E. Avignone, W. Même, A. Koulakoff, L. Venance, F. Blomstrand, and C. Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol. 94, no. 7-8, pp. 457-475, 2002.

[6] J. Hjorth, K. T. Blackwell, and J. Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J. Neuroscience, vol. 29, no. 16, pp. 5276-5286, 2009.

[7] R. D. Traub, M. A. Whittington, E. H. Buhl, F. E. N. LeBeau, A. Bibbig, S. Boyd, H. Cross, and T. Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol. 42, no. 2, pp. 153-170, 2001.
\\
\hline
\end{longtable}

\clearpage
In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
stimulation with an array of 50 NW connections per neuron. The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations. We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.

\textbf{Gap Junction Interface [4]}:

With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells. Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity. In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted. This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.

\begin{figure}[H]
\centering
\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
\label{new_1}
\end{figure}

\end{document}
